Dynein project log

### 2016-12-31 thesis_stuff/thesis_stuff.tex
Add yet another paper to thesis_stuff.tex, which says that maybe cm changes between one/bothbound.

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine\\\hline
    $L_s$ & 12nm & & & 21.0nm & 22.1nm &\\ \hline
    $L_t$ &  7nm & & & & 11.15nm &\\ \hline
    $R_b$ &  & & & 1.57nm & 1.45nm &\\ \hline
    $R_m$ &  7nm & & & 7.36nm & 6.3nm &\\ \hline
    $R_t$ &  & & & & 2.16nm & \\ \hline
    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & \\ \hline
    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & &\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & &\\ \hline
    $\theta_{t}$ & 0$^{\circ}$ & & & & &\\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ & & & & &\\ \hline
    $k_b$ & $5000 s^{-1,b}$ & & & & &\\ \hline
    $\Delta G_{bind, bb}$ & & & & & & -71 kJ/mol\\ \hline
    $\Delta G_{bind, ob}$ & & & & & & -37 kJ/mol\\ \hline
    $c_t$ & & & & & & \\ \hline
    $c_m$ & & & & & & \\ \hline
    $c_b$ & & & & & & 140 kJ/mol\\ \hline
  \end{tabular}
\end{center}

@@

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{2cm} | p{5cm} |}
    \hline
    Ls & Lt & kb & kub & cm & cb & ct & $\Big<P(\mbox{unbind per dt})\Big>$ & $\Big<\mbox{step time}\Big>$ & errors\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.02 & 0.02 & 0.02 & NA      & NA     & keeled over after ns \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & $9e-9 $ & 1.7e-4 & keeled over after ns\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.18 & 0.18 & 0.18 & $4e-9 $ & 3.4e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & $3e-9 $ & 2.9e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.58 & 0.58 & 0.58 & $2e-10$ & 3.3e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & $6e-12$ & 8.4e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.74 & 1.74 & 1.74 & $1e-13$ & 3.3e-3 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.32 & 2.32 & 2.32 & $7e-16$ & 7.8e-3 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.90 & 2.90 & 2.90 & $2e-18$ & ?? & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 3.49 & 3.49 & 3.49 & $5e-21$ & ?? & no error yet\\\hline
    22.1 & 11.1 & 2500 & 5000 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
    22.1 & 11.1 & 1500 & 5000 & 3.32 & 3.32 & 3.32 & ?? & ?? & \\\hline
    22.1 & 11.1 &  500 & 5000 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
    22.1 & 11.1 &  100 & 5000 & 3.32 & 3.32 & 3.32 & ?? & ?? & \\\hline
  \end{tabular}
\end{center}

@@

>>>>

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess\\\hline
    $L_s$ & 12nm & & & 21.0nm & 22.1nm & & & \\ \hline
    $L_t$ &  7nm & & & & 11.15nm & & & \\ \hline
    $R_b$ &  & & & 1.57nm & 1.45nm & & & \\ \hline
    $R_m$ &  7nm & & & 7.36nm & 6.3nm & & & \\ \hline
    $R_t$ &  & & & & 2.16nm & & & \\ \hline
    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & & & 160\\ \hline
    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & & & & 136\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & & & & \\ \hline
    $\theta_{t}$ & 0$^{\circ}$ & & & & & & & \\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ & & & & & & $90.2 \pm 4.5$& \\ \hline
    $k_b$ & $5000 s^{-1,b}$ & & & & & & & \\ \hline
    $\Delta G_{bind, bb}$ & & & & & & -71 kJ/mol & & \\ \hline
    $\Delta G_{bind, ob}$ & & & & & & -37 kJ/mol & & \\ \hline
    $c_t$ & & & & & & & & \\ \hline
    $c_m$ & & & & & & & & \\ \hline
    $c_b$ & & & & & & 140 kJ/mol & & \\ \hline
  \end{tabular}
\end{center}

@@

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{2cm} | p{5cm} |}
    \hline
    Ls & Lt & kb & kub & cm & cb & ct & $\Big<P(\mbox{unbind per dt})\Big>$ & $\Big<\mbox{step time}\Big>$ & errors\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.02 & 0.02 & 0.02 & NA      & NA     & keeled over after ns \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & $9e-9 $ & 1.7e-4 & keeled over after ns\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.18 & 0.18 & 0.18 & $4e-9 $ & 3.4e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & $3e-9 $ & 2.9e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.58 & 0.58 & 0.58 & $2e-10$ & 3.3e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 3500 & 1.00 & 1.00 & 1.00 & ?? & ?? & \\\hline
    22.1 & 11.1 & 5000 & 2000 & 1.00 & 1.00 & 1.00 & ?? & ?? & unknown error??\\\hline
    22.1 & 11.1 & 5000 & 1000 & 1.00 & 1.00 & 1.00 & ?? & ?? & unknown error??\\\hline
    22.1 & 11.1 & 5000 &  100 & 1.00 & 1.00 & 1.00 & ?? & ?? & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & $6e-12$ & 8.4e-4 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.74 & 1.74 & 1.74 & $1e-13$ & 3.3e-3 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.32 & 2.32 & 2.32 & $7e-16$ & 9.0e-3 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 3500 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
    22.1 & 11.1 & 5000 & 2000 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
    22.1 & 11.1 & 5000 & 1000 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
    22.1 & 11.1 & 5000 &  100 & 2.32 & 2.32 & 2.32 & ?? & ?? & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.90 & 2.90 & 2.90 & $2e-18$ & 7.2e-2 & no error yet\\\hline
    22.1 & 11.1 & 5000 & 5000 & 3.49 & 3.49 & 3.49 & $5e-21$ & ?? & no error yet\\\hline
  \end{tabular}
\end{center}

@@

A FRET study on how ATP changes the distance of domains. They label the C-terminal tail and different regions on the motor, then calculate the FRET efficiency. FRETY efficiency is higher when ATP is present, indicating two different states based on ATP presence. They try to trap dynein in different states (apo, ATP, ADP-Pi, ADP) using different trapping nucleotide analogs. ADP-Vi dynein stayed in state II, while nonhydrolyzable ATP, apo, and ADP additions caused the motor to stay in state I.\\

The interpretation is that the dynein's tail moves from a state where it is near the C-terminus (AAA5) to one where it is near AAA2. 5->2 is prestroke on hydrolysis, 2->5 is poststroke on Pi rejection. ATP binding is what causes the conformation change, since they have trapped ATP-ish bound dyneins in both state I and II. The powerstroke happens during the ADP state, since they have an ADP-dynein in state II and another in state I.\\

They also report an ATPase $k_{cat} = 90.2 \pm 4.5$, meaning roughly 100 ATP are cycled per second.\\

\subsection{Possibly more equilibrium motor angles}
Dynein structure and power stroke
Nature 2003, Burgess and Oiwa

EM microscopy of apo/ADP-Vi flagellar dynein shows that the stem and stalk don't change length between two states, only the angle/position changes. The paper claims ``the origin of the movement is a displacement of the stem relative to the head and stalk.''.

Paper claims motor angle is \textbf{160 degrees in pre-stroke and 136 degrees in powerstroke}.\\

There is a difference in standard deviation of angles in pre/post-stroke. Pre-stroke has a stdev of 20 degrees, Post-stroke has a stdev of 11. The authors indicate this is due to stiffening of the stalk/foot domain. This seems like it would indicate changes in the motor spring constants between the pre/post-powerstroke states.
